Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-01-28 shortfollowup.tex
Added EGA citation; removed old todos. Only the proof of 3.5 is missing.

\begin{abstract}
We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes
over finite fields.  In previous work, we considered the case of commutative smooth group schemes and found
that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  In this paper,
we give a modification of the category of character sheaves that remedies this defect, and is also extensible to
non-commutative groups.  
As an application, we use these \emph{commutative character sheaves} to geometrize types for
supercuspidal representations of $p$-adic groups. 
\end{abstract}

@@

Finally, we use the category $\CCS(G)$ to give a geometric description of generic types for supercuspidal representations
of connected reductive groups over local fields.  In this way, we provide all of the ingredients
needed to parametrize supercuspidal representations of arbitrary depth in the same category:
perverse sheaves on group schemes over finite fields. \todo{Update based on any changes in Section 4}

@@

\todo{Add summary of Section 4 once it has stabilized}

@@

Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \todo{include reference for this definition}.
This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
$\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.

@@

%\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
By \cite{demazure:SGA3-VIA}*{Thm. 3.2}, the abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ and the quotient $q: G \to G\ab$ is a $G\der$-torsor in the fppf topology.
%
To simplify notation below, set $H=G\der$
and let $j : H\hookrightarrow G$ be the inclusion. 
With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
 \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
%
Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
it is also an $H$-torsor in the fpqc topology.
It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
%
On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
This completes the proof of Proposition~\ref{prop:Gder_triv}.
%\end{proof}

>>>>

\begin{abstract}
We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes
over finite fields.  In previous work, we considered the case of commutative smooth group schemes and found
that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  In this paper,
we give a modification of the category of character sheaves that remedies this defect, and is also extensible to
non-commutative groups.   
\end{abstract}

@@

Finally, we use the category $\CCS(G)$ to give a geometric description of generic types for supercuspidal representations
of connected reductive groups over local fields.  In this way, we provide all of the ingredients
needed to parametrize supercuspidal representations of arbitrary depth in the same category:
perverse sheaves on group schemes over finite fields.

@@

@@

Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGA:IV4}*{Def 17.3.1}. This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
$\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.

@@

%\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
By \cite{demazure:SGA3-VIA}*{Thm. 3.2}, the abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ and the quotient $q: G \to G\ab$ is a $G\der$-torsor in the fppf topology.
%
To simplify notation below, set $H=G\der$
and let $j : H\hookrightarrow G$ be the inclusion. 
With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
 \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
%
Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
it is also an $H$-torsor in the fpqc topology.
It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
%\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
%
On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
This completes the proof of Proposition~\ref{prop:Gder_triv}.
%\end{proof}
